Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-01-29 Manuscript/TEM_draft.tex
Updated comments

%Hummm Nick's comment again - That's a point to make in the discussion maybe. But let's wait for Gavin comments...
%it's possible that adding dating information etc. in tip-dating makes Bayesian dated total-evidence analyses (ie tip-dating) better than non-dated Bayesian total-evidence analyses (typical total-evidence approach), because more information is being used, and because dates give some information about phylogenetic position.  In any case, the study wasn't about tip-dating
% NC: Simplest thing here is to just leave out the mention of tip dating. Will need to fix in discussion
% NC: Also Nick makes another sensible comment about *why* are living species more important. Check this is covered in discussion

@@

Although missing data does not appear be a major problem in molecular and morphological matrices separately (as long as enough data overlaps in each case)
%G: Might be worthing reading and citing this: http://www.sciencemag.org/content/333/6041/448.full. Missing data can be a problem if it renders some subtrees unresolvable. TG: added citation in the whole bunch.
% NC: Did you actually *read* this paper? It makes the point that it *is* a problem if it affects certain subtrees. Might need to add a small caveat into the bit in brackets above...
 \citep{wiensmissing2003,wiensmissing2006,wiensmissing2008,rouresite-specific2011,Sanderson22072011,pattinsonphylogeny2014}, it may become more of an issue in Total Evidence matrices containing both molecular and morphological data for living and fossil taxa. This may be particularly problematic as fossil taxa (generally) do not have molecular data, resulting in a large section of missing data in Total Evidence matrices. Until now, no attempt has been made to study the impact of this issue on phylogenetic inference using Total Evidence methods.

@@

Here we use a simulation approach to assess the effect of missing data on tree topologies inferred from Total Evidence matrices. Since the molecular part of a Total Evidence matrix acts like a "classical" molecular matrix containing only the living taxa \citep{ronquista2012}, the effect of missing data on such matrices is well known \citep{wiensmissing2006,wiensmissing2008,lemmonthe2009,rouresite-specific2011}.
%G: Alan Lemmon has done a fair amount of work on missingness - worth checking out the work from his lab, e.g. http://www.evotutor.org/LemmonLab/Pdfs/Lemmon-etal2009.pdf TG: added reference (that was actually in the 2014 draft)
% NC: OK. But be careful here. When people give you comments you want to take them seriously and actually read the papers they suggest rather than just adding references. Are you sure Lemmon is just looking at molecular stuff? Think Gavin's point might be that he's done stuff on missingness in morphological data too which at present we don't really cite or cover at all.
 Therefore, we focus only on missing data in the morphological part of the matrix. We investigate three major parameters that directly affect the completeness and size of the morphological part of the matrix: (i) the proportion of living taxa with no morphological data; (ii) the proportion of missing data in the fossil taxa; and (iii) the proportion of missing morphological characters for both living and fossil taxa in the matrix (i.e. the size of the matrix). These parameters reflect empirical biases in data availability as follows: (i)
% NC: The next few sentences could be moved to the methods. They feel a bit clunky here. TG: I like the way they end the intro: "we're simulating stuff but it links to more real stuff in reality."
% NC: OK but hey currently don't make sense in terms of what was said perviosuly so I've numbered them. Still don't like this. It really should be integrated with the parameters. Basically it's poorly structured and doesn't follow very well - that's what I mean by "clunky"
the increased availability of molecular data
% NC: Not really the molecular clock, actually more the ease of extracting DNA. 
means that morphological data for living species is rarely collected, and few people have the skills to identify characters needed for detailed phylogenetic analysis; (ii) missing data in fossil taxa is common due to preservation biases \citep{sansomfossilization2013}; and (iii) the overall number of characters depends on the effort of the people identifying them \citep[e.g.][]{O'Leary08022013}. We remove data from a Total Evidence matrix by changing the values of these three parameters and then assess how this affects the topology of trees inferred using Maximum Likelihood and Bayesian methods. We find that the ability of Total Evidence methods to recover the "best" tree topology is increased when using Bayesian methods. Also minimizing the number of living taxa with no morphological data and the number of missing morphological characters improves the ability of Total Evidence methods to recover the "best" tree topology more so than minimizing the amount of missing data in the fossil record.

@@

\subsection{1. Generating the matrix}
\label{Generating_the_matrix}
First we randomly generated a "true" tree of 50 taxa in R v. 3.0.2 \citep{R302} using the package diversitree v. 0.9-6 \citep{fitzjohndiversitree2012}. We generated the tree using a birth death process by sampling speciation ($\lambda$) and extinction ($\mu$) rates from a uniform distribution but maintaining $\lambda$ $>$ $\mu$ \citep{paradistime-dependent2011}. We implemented a rejection sampling algorithm to select only trees with 25 living and 25 fossil taxa 
%G:I don’t think there is a problem with this split but I expect reviewers might ask for justification. Is this typical of existing TE studies? TG: avoiding bias comment.
% NC: I think you misunderstood Gavin's point. He knows why you did it like this, but if usually TE studies are 95% living and 5% fossil (for example) then your results aren't really viable in real world. He ideally wants a statement like: this is a typical split between fossil and living tax across empirical TE studies (cite papers). However, I doubt this is the case. Actually aren't TE studeis usually dominated by fossil taxa?
to ensure that we had enough taxa of each type for our simulations to work, and to avoid any bias toward fossil or living taxa. We then added an outgroup to the tree, using the mean branch length of the tree to separate the outgroup from the rest of the taxa, and with the branch length leading to the outgroup set as the sum of the mean branch length and the longest root-to-tip length of the tree.

@@

\begin{enumerate}
\item{$M_{L}$, the proportion of living taxa with no morphological data: 0\%, 10\%, 25\%, 50\% or 75\%.}
This parameter illustrates the number of living taxa that are present in the molecular part of the matrix but not in the morphological part. This reflects the fact that detailed morphological data for living species are scarce.
\item{$M_{F}$, the proportion of missing data in the fossil taxa: 0\%, 10\%, 25\%, 50\% or 75\%.}
This parameter illustrates the quality of the fossil record. 
\item{$M_{C}$, the proportion of missing morphological characters for both living and fossil taxa: 0\%, 10\%, 25\%, 50\% or 75\%. }
This parameter illustrates the number of available morphological characters for both living and fossil taxa.
\end{enumerate}

@@

To measure the support for each branch in our simulated phylogenies
%G: Do you mean you tested whether the simulated data generally had any phylogenetic signal with which to recover a tree? I was a bit unsure but mainly because I am hardwired to thinks of Pagel’s lambda when anyone mentions phylogenetic signal…
% NC: Haha that is exactly what I've said about a million times to you.
we first ran a fast bootstrap analysis (Lazy Sub-tree Rearrangement) with 500 replicates on the "complete" matrix. We removed all the simulations with a median bootstrap support lower than 50 as a proxy for weak phylogenetic signal \citep{zanderminimal2004}. We repeated this selection until we obtained 50 sets of simulations (i.e. 50 "complete" and 50 x 125 "missing-data" matrices) with a relative good phylogenetic signal (median bootstrap $>$ 50). On these selected simulations, we used the fast bootstrap algorithm and performed 1000 bootstraps for each tree inference to assess topological support \citep{pattengale2010many}. Using these parameters took \texttildelow 8 CPU years to build 50 sets of 125 bootstrapped Maximum Likelihood trees (2.30GHz clock speed nodes).

@@

\subsection{4. Comparing topologies}
We compared the topology of the "missing-data" trees to the "best" tree to measure the effect of the three parameters $M_{L}$, $M_{F}$ and $M_{C}$ on tree topology. We used the Robinson-Foulds distance \citep{RF1981} to assess the amount of conserved clade positions and the Triplets distance \citep{dobson1975triplets} to assess the amount of wildcard taxa (i.e. taxa that frequently change position in different trees; \citealt{kearneyfragmentary2002}).
%G: Why these two metrics? Might need a few sentences to justify them in addition to the explanation of what they are that you already have.
We used these metrics because they are widely used in literature \citep{Bogdanowicz2012}, their relative performance is well described \citep{Kuhner04112014} % NC: Is that what you mean. "they relative performance" means nothing to me.
and because they illustrate two different aspects of tree topology (see Discussion).
We normalised both metrics using methods described in \citet{Bogdanowicz2012} to generalize our results for any \textit{n} number of taxa. These metrics are described in detail below.

@@

% NC: Yes BUT the point is that Gavin misunderstood so you need to be clearer! Add a comment earlier that points out that the Bayesian consensus trees are not fully resolved (if this is true). If they are fully resolved more often than the ML trees you may need t oadd a paragraph to the discussion as Gavin is right, this could explain the result.
The effect of the missing data in the fossil record ($M_{F}$) is less than the effect of the $M_{L}$ parameter on clade conservation (Normalised Robinson-Foulds distance) but greater on the displacement of wildcard taxa (Normalised Triplets distance; Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). This is related to the fact that the Bayesian consensus tree is built using a majority consensus rule. When the fossil taxa have less data (e.g. $M_{F}$ = 75\%) they will tend to branch with any taxon in the clade that shares most characters with the fossils. Therefore a majority consensus position is unlikely to exist (i.e. every branching position is represented in $<$ 50\% of the trees in the Bayesian posterior distribution) and the fossil taxa will form a polytomy at the base of the clade. This does not decrease the Normalised Robinson-Foulds distance, because clades are conserved, but decreases the Normalised Triplets distance because the fossils act as wildcard taxa. Conversely, the same scenario in a Maximum Likelihood framework will lead to a dichotomous branching of the fossils but with low bootstrap support ($<$ 50). In other words, the Bayesian consensus tree allows a fossil taxon with few data to be placed with a higher confidence at a lower taxonomic level than the Maximum Likelihood tree, where the fossil will be placed with lower confidence at a higher taxonomic level. We argue that using the Bayesian consensus tree topology is preferable because it is more conservative \cite[e.g][]{pattinsonphylogeny2014}.

@@

\subsection{Combined effect of missing data parameters}
As expected, when combining the missing data parameters, our ability to recover the "best" tree topology is affected in the same way as for the parameters individually: the Normalised Robinson-Foulds distance and the Normalised Triplets distance are higher when all the missing data parameters have few missing data (i.e. $M_{L}$ = 0\%, $M_{F}$ = 0\%, $M_{C}$ = 0\%) and lower when they have a lot of missing data (i.e. $M_{L}$ = 75\%, $M_{F}$ = 75\% and $M_{C}$ = 75\%; Fig.~\ref{Fig_Results-global_perparam}). However, it is important to notice that the effect of each parameter is not additive. The number of missing living taxa with morphological data ($M_{L}$) and the overall number of missing morphological characters ($M_{C}$), have a bigger effect than the amount of missing data for the fossil taxa ($M_{F}$), and when both $M_{L}$ and $M_{C}$ reach 50\% of missing data, the matrix does not contain enough phylogenetic information for the fossil taxa to be placed with confidence in the tree (Fig.~\ref{Fig_Results-paircomp_within}). This has important implications for building Total Evidence phylogenies (see below).

@@

% NC: These are still really hard to follow but I'm at a loss as to how to explain them better.

>>>>

%Hummm Nick's comment again - That's a point to make in the discussion maybe. But let's wait for Gavin comments...
%it's possible that adding dating information etc. in tip-dating makes Bayesian dated total-evidence analyses (ie tip-dating) better than non-dated Bayesian total-evidence analyses (typical total-evidence approach), because more information is being used, and because dates give some information about phylogenetic position.  In any case, the study wasn't about tip-dating
% NC: Simplest thing here is to just leave out the mention of tip dating. Will need to fix in discussion
% NC: Also Nick makes another sensible comment about *why* are living species more important. Check this is covered in discussion 
%TG: I think that's covered in \subsection{Individual effects of missing data parameters} - \subsubsection{Missing data for living taxa ($M_{L}$)}. (If no living taxa, the fossils cannot branch.)

@@

Although missing data does not appear be a major problem in molecular and morphological matrices separately (as long as enough data overlaps in each case)
%G: Might be worthing reading and citing this: http://www.sciencemag.org/content/333/6041/448.full. Missing data can be a problem if it renders some subtrees unresolvable. TG: added citation in the whole bunch.
% NC: Did you actually *read* this paper? It makes the point that it *is* a problem if it affects certain subtrees. Might need to add a small caveat into the bit in brackets above... TG: Ok, so this comment goes with the data overlap. I’m not entirely sure where the paper comes in. If the there is not enough overlap in the super matrix, then it is impossible to get a consensus clade tree (kind of supporter talked in the paper) per terrace?
 \citep{wiensmissing2003,wiensmissing2006,wiensmissing2008,rouresite-specific2011,pattinsonphylogeny2014}, it may become more of an issue in Total Evidence matrices containing both molecular and morphological data for living and fossil taxa. This may be particularly problematic as fossil taxa (generally) do not have molecular data, resulting in a large section of missing data in Total Evidence matrices. Until now, no attempt has been made to study the impact of this issue on phylogenetic inference using Total Evidence methods.

@@

Here we use a simulation approach to assess the effect of missing data on tree topologies inferred from Total Evidence matrices. Since the molecular part of a Total Evidence matrix acts like a "classical" molecular matrix containing only the living taxa \citep{ronquista2012}, the effect of missing data on such matrices is well known \citep{wiensmissing2006,wiensmissing2008,lemmonthe2009,rouresite-specific2011}.
%G: Alan Lemmon has done a fair amount of work on missingness - worth checking out the work from his lab, e.g. http://www.evotutor.org/LemmonLab/Pdfs/Lemmon-etal2009.pdf TG: added reference (that was actually in the 2014 draft)
% NC: OK. But be careful here. When people give you comments you want to take them seriously and actually read the papers they suggest rather than just adding references. Are you sure Lemmon is just looking at molecular stuff? Think Gavin's point might be that he's done stuff on missingness in morphological data too which at present we don't really cite or cover at all. TG: I don’t like arguing on comments but this paper is about missing data in molecular matrices (still relevant though). The reason I removed it from the old version is that it states something kind of similar than all the others: overlap but it is specially important in bigger matrices where missing data can weaken the support in certain parts of the tree. The idea being probably close to the tree terrace paper.
Therefore, we focus only on missing data in the morphological part of the matrix. We investigate three major parameters that directly affect the completeness and size of the morphological part of the matrix: (i) the proportion of living taxa with no morphological data; (ii) the proportion of missing data in the fossil taxa; and (iii) the proportion of missing morphological characters for both living and fossil taxa in the matrix (i.e. the size of the matrix).
% NC: The next few sentences could be moved to the methods. They feel a bit clunky here. TG: I like the way they end the intro: "we're simulating stuff but it links to more real stuff in reality."
% NC: OK but hey currently don't make sense in terms of what was said perviosuly so I've numbered them. Still don't like this. It really should be integrated with the parameters. Basically it's poorly structured and doesn't follow very well - that's what I mean by "clunky"  - TG: You're right (as usual ;)) it works better without.
%These parameters reflect empirical biases in data availability as follows: (i) the increased availability of molecular data means that morphological data for living species is rarely collected, and few people have the skills to identify characters needed for detailed phylogenetic analysis; (ii) missing data in fossil taxa is common due to preservation biases \citep{sansomfossilization2013}; and (iii) the overall number of characters depends on the effort of the people identifying them \citep[e.g.][]{O'Leary08022013}.
We remove data from a Total Evidence matrix by changing the values of these three parameters and then assess how this affects the topology of trees inferred using Maximum Likelihood and Bayesian methods.
%TG: I swapped the results to be consistent, ML and MC first and then Bayesian
We find that minimizing the number of living taxa with no morphological data and the number of missing morphological characters improves the ability of Total Evidence methods to recover the "best" tree topology more so than minimizing the amount of missing data in the fossil record. Additionally, we find that the ability of Total Evidence methods to recover the "best" tree topology is increased when using Bayesian methods.

@@

\subsection{1. Generating the matrix}
\label{Generating_the_matrix}
First we randomly generated a "true" tree of 50 taxa in R v. 3.0.2 \citep{R302} using the package diversitree v. 0.9-6 \citep{fitzjohndiversitree2012}. We generated the tree using a birth death process by sampling speciation ($\lambda$) and extinction ($\mu$) rates from a uniform distribution but maintaining $\lambda$ $>$ $\mu$ \citep{paradistime-dependent2011}.
%G:I don’t think there is a problem with this split but I expect reviewers might ask for justification. Is this typical of existing TE studies? TG: avoiding bias comment.
% NC: I think you misunderstood Gavin's point. He knows why you did it like this, but if usually TE studies are 95% living and 5% fossil (for example) then your results aren't really viable in real world. He ideally wants a statement like: this is a typical split between fossil and living tax across empirical TE studies (cite papers). However, I doubt this is the case. Actually aren't TE studeis usually dominated by fossil taxa?
% TG: Really depends. In the 5 I keep citing, Pyron is close to 50/50, Ronquist and Slater are more towards living and Beck is more towards fossil
Empirical Total Evidence matrices can be biased towards a greater number of fossils (e.g. 88\% and 58\% fossils taxa in respectively \citealt{beckancient2014} and \citealt{schragocombining2013}) or towards more living taxa (e.g. 69\% of living taxa in both \citealt{ronquista2012} and \citealt{slaterphylogenetic2013}) buy they can contain an even number of both type of taxa (e.g. 52\% of living taxa in \citealt{pyrondivergence2011}). Therefore, to avoid biasing our simulations towards the two extreme situations (more living or fossil taxa) and to make each simulation comparable, we implemented a rejection sampling algorithm to select only trees with 25 living and 25 fossil taxa.
We then added an outgroup to the tree, using the mean branch length of the tree to separate the outgroup from the rest of the taxa, and with the branch length leading to the outgroup set as the sum of the mean branch length and the longest root-to-tip length of the tree.

@@

%TG: this part was removed from the into: These parameters reflect empirical biases in data availability as follows: (i) the increased availability of molecular data means that morphological data for living species is rarely collected, and few people have the skills to identify characters needed for detailed phylogenetic analysis; (ii) missing data in fossil taxa is common due to preservation biases \citep{sansomfossilization2013}; and (iii) the overall number of characters depends on the effort of the people identifying them \citep[e.g.][]{O'Leary08022013}.

\begin{enumerate}
\item{$M_{L}$, the proportion of living taxa with no morphological data: 0\%, 10\%, 25\%, 50\% or 75\%.}
This parameter illustrates the number of living taxa that are present in the molecular part of the matrix but not in the morphological part. This reflects the fact that morphological data for living species are scarce. This can be due to the increased availability of molecular data and/or that few people have the skills to identify characters needed for detailed phylogenetic analysis.
\item{$M_{F}$, the proportion of missing data in the fossil taxa: 0\%, 10\%, 25\%, 50\% or 75\%.}
This parameter illustrates the quality of the fossil record. 
\item{$M_{C}$, the proportion of missing morphological characters for both living and fossil taxa: 0\%, 10\%, 25\%, 50\% or 75\%. }
This parameter illustrates the number of available morphological characters for both living and fossil taxa. This reflects the amount of effort put into identifying the characters \citep[e.g.][]{O'Leary08022013}.
\end{enumerate}

@@

To measure the support for each branch in our simulated phylogenies
%G: Do you mean you tested whether the simulated data generally had any phylogenetic signal with which to recover a tree? I was a bit unsure but mainly because I am hardwired to thinks of Pagel’s lambda when anyone mentions phylogenetic signal…
% NC: Haha that is exactly what I've said about a million times to you.
% TG: And after the literature review for the next paper (missing living in mammals) on community structure & Co. I start to get where you guys are comming for ;).
we first ran a fast bootstrap analysis (Lazy Sub-tree Rearrangement) with 500 replicates on the "complete" matrix. We removed all the simulations with a median bootstrap support lower than 50 as a proxy for weak phylogenetic signal \citep{zanderminimal2004}. We repeated this selection until we obtained 50 sets of simulations (i.e. 50 "complete" and 50 x 125 "missing-data" matrices) with a relative good phylogenetic signal (median bootstrap $>$ 50). On these selected simulations, we used the fast bootstrap algorithm and performed 1000 bootstraps for each tree inference to assess topological support \citep{pattengale2010many}. Using these parameters took \texttildelow 8 CPU years to build 50 sets of 125 bootstrapped Maximum Likelihood trees (2.30GHz clock speed nodes).

@@

\subsection{4. Comparing topologies}
We compared the topology of the "missing-data" trees to the "best" tree to measure the effect of the three parameters $M_{L}$, $M_{F}$ and $M_{C}$ on tree topology. We used the Robinson-Foulds distance \citep{RF1981} to assess the amount of conserved clade positions and the Triplets distance \citep{dobson1975triplets} to assess the amount of wildcard taxa (i.e. taxa that frequently change position in different trees; \citealt{kearneyfragmentary2002}).
%G: Why these two metrics? Might need a few sentences to justify them in addition to the explanation of what they are that you already have.
%We used these metrics because they are widely used in literature \citep[][e.g.]{Bogdanowicz2012}, their relative performance is well described \citep{Kuhner04112014} % NC: Is that what you mean. "they relative performance" means nothing to me. 
%and because they illustrate two different aspects of tree topology (see Discussion). TG: ok I've fixed that towards: "as said above, they describe two different things but also they're cool because we know how they behave and the code is available to calculate them." - a bit more honest.
We used these two metrics because they illustrate two different aspects of tree topology (see Discussion) but also because their performance in measuring differences in topology is well described \citep{Kuhner04112014} and well implemented \citep{Bogdanowicz2012}.
We normalised both metrics using methods described in \citet{Bogdanowicz2012} to generalize our results for any \textit{n} number of taxa. These metrics are described in detail below.

@@

% NC: Yes BUT the point is that Gavin misunderstood so you need to be clearer! Add a comment earlier that points out that the Bayesian consensus trees are not fully resolved (if this is true). If they are fully resolved more often than the ML trees you may need t oadd a paragraph to the discussion as Gavin is right, this could explain the result. TG: this is now explained in the following paragraph after this one mentioning in details the polytomy stuff. Or should be coming before?
The effect of the missing data in the fossil record ($M_{F}$) is less than the effect of the $M_{L}$ parameter on clade conservation (Normalised Robinson-Foulds distance) but greater on the displacement of wildcard taxa (Normalised Triplets distance; Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). This is related to the fact that the Bayesian consensus tree is built using a majority consensus rule. When the fossil taxa have less data (e.g. $M_{F}$ = 75\%) they will tend to branch with any taxon in the clade that shares most characters with the fossils. Therefore a majority consensus position is unlikely to exist (i.e. every branching position is represented in $<$ 50\% of the trees in the Bayesian posterior distribution) and the fossil taxa will form a polytomy at the base of the clade. This does not decrease the Normalised Robinson-Foulds distance, because clades are conserved, but decreases the Normalised Triplets distance because the fossils act as wildcard taxa. Conversely, the same scenario in a Maximum Likelihood framework will lead to a dichotomous branching of the fossils but with low bootstrap support ($<$ 50). In other words, the Bayesian consensus tree allows a fossil taxon with few data to be placed with a higher confidence at a lower taxonomic level than the Maximum Likelihood tree, where the fossil will be placed with lower confidence at a higher taxonomic level. We argue that using the Bayesian consensus tree topology is preferable because it is more conservative \cite[e.g][]{pattinsonphylogeny2014}.

Also, because the Bayesian consensus tree are more likely to contain polytomies when some branching are poorly resolved (in $<$ 50\% of the trees) in the "best" tree, the Bayesian consensus "missing-data" trees have a higher probability to be less distant to the "best" tree than in a Maximum Likelihood framework. However we minimized this effect by only selecting matrices that had a median bootstrap for all their nodes $>$ 50 (see Methods, section 3).

@@

\subsection{Combined effect of missing data parameters}
As expected, when combining the missing data parameters, our ability to recover the "best" tree topology is affected in the same way as for the parameters individually: the Normalised Robinson-Foulds distance and the Normalised Triplets distance are higher when all the missing data parameters have few missing data (i.e. $M_{L}$ = 0\%, $M_{F}$ = 0\%, $M_{C}$ = 0\%) and lower when they have a lot of missing data (i.e. $M_{L}$ = 75\%, $M_{F}$ = 75\% and $M_{C}$ = 75\%; Fig.~\ref{Fig_Results-global_perparam}). However, it is important to notice that the effect of each parameter is not additive. The number of missing living taxa with morphological data ($M_{L}$) and the overall number of missing morphological characters ($M_{C}$), have a bigger effect than the amount of missing data for the fossil taxa ($M_{F}$), and when both $M_{L}$ and/or $M_{C}$ reach 50\% of missing data, the matrix does not contain enough phylogenetic information for the fossil taxa to be placed with confidence in the tree (Fig.~\ref{Fig_Results-paircomp_within}).

@@

% NC: These are still really hard to follow but I'm at a loss as to how to explain them better.
% TG: will the t-test analogy be useful here?
